Sequential rank agreement methods for comparison of lists

### 2015-08-08 latex/paper.Rnw
More comment fixing

A not expected shape of the agreement curves is seen for the Ridge
models for all three tuning criteria. They all show higher
disagreement in the top of the lists followed by a decrease. The
reason behind this behavior is rather subtle. Looking at the
distribution of the regression coefficients we see that a large
proportion of them are numerically very close to zero and have almost
equal absolute value. This is a general feature of the Ridge models in
this data set and seen for all the 1000 trained models.
This implies that when predictors are ranked according to the
magnitude of their coefficients, their actual order becomes more
uncertain and more close to a random permutation. This problem can be
alleviated by artificially censoring all predictors with absolute
coefficient values below a given threshold. For the Ridge models tuned
with the deviance criterion, Figure \ref{fig:app2} (left) shows the
the sequential rank agreement where for each of the 1000 trained
models predictors were artificially censored when their absolute
coefficient value was lower than the $0.1\%$ quantile of the 5000
absolute coefficient values. The corresponding curve from Figure
\ref{fig:app1} (left panel) is shown for comparison.
%%%% CHECK UP: CENSOR ON POOLED DATA OR CENSOR BY INVIDIAL THRESHOLD

%%%%%% DET HER ER NOGET ROD. DER ER FORSVUNDET NOGET LASSO TEKST
%%%%%% GÅ TILBAGE OG FIND DET IGEN
Under the deviance optimization criterion the median number of non-zero 
coefficients was 33 (range 18 to 52). In order to calculate the sequential 
rank agreement for the Lasso we therefore applied our proposed Algorithm \ref{sra-algorithm}
with $B = 1000$ and $P=5000$.

>>>>

A not expected shape of the agreement curves is seen for the Ridge
models for all three tuning criteria. They all show higher
disagreement in the top of the lists followed by a decrease. The
reason behind this behavior is rather subtle. Looking at the
distribution of the regression coefficients we see that a large
proportion of them are numerically very close to zero and have almost
equal absolute value. This is a general feature of the Ridge models in
this data set and seen for all the 1000 trained models.
This implies that when predictors are ranked according to the
magnitude of their coefficients, their actual order becomes more
uncertain and more close to a random permutation. This problem can be
alleviated by artificially censoring all predictors with absolute
coefficient values below a given threshold. For the Ridge models tuned
with the deviance criterion, Figure \ref{fig:app2} (left) shows the
the sequential rank agreement where for each of the 1000 trained
models predictors were artificially censored when their absolute
coefficient value was lower than the $0.1\%$ quantile of the 5000
absolute coefficient values. The corresponding curve from Figure
\ref{fig:app1} (left panel) is shown for comparison.
\textbf{CHECK UP: CENSOR ON POOLED DATA OR CENSOR BY INDIVIDUAL THRESHOLD}

\textbf{DET HER ER NOGET VÆRRE ROD. DER ER FORSVUNDET NOGET LASSO TEKST. GÅ TILBAGE OG FIND DET IGEN}
Under the deviance optimization criterion the median number of non-zero 
coefficients was 33 (range 18 to 52). In order to calculate the sequential 
rank agreement for the Lasso we therefore applied our proposed Algorithm \ref{sra-algorithm}
with $B = 1000$ and $P=5000$.
